Some usefull words/expressions/sentences

### 2018-06-25 paper/main.tex
references added, R code some, paper template confirmed

\addbibresource{example.bib} % The filename of the bibliography

@@

\vspace*{.06\textheight}
{\scshape\Huge \bfseries \univname\par}\vspace{1.5cm} % University name
\textsc{\Large MSc Project Report \\ 2017-2018}\\[0.5cm] % Thesis type

\HRule \\[0.4cm] % Horizontal line
{\Large \bfseries \ttitle\par}\vspace{0.4cm} % Thesis title
\HRule \\[1.5cm] % Horizontal line

\begin{minipage}[t]{0.4\textwidth}
\begin{flushleft} \large
\emph{Author:}\\
\href{wangcc.me}{\authorname} % Author name - remove the \href bracket to remove the link
\end{flushleft}
\end{minipage}
\begin{minipage}[t]{0.4\textwidth}
\begin{flushright} \large
\emph{Supervisor:} \\
\href{https://www.lshtm.ac.uk/aboutus/people/palla.luigi}{\supname} % Supervisor name - remove the \href bracket to remove the link
\end{flushright}
\end{minipage}\\[3cm]

>>>>

\addbibresource{summer.bib} % The filename of the bibliography

@@

\vspace*{.06\textheight}
{\scshape\huge \bfseries \univname\par}\vspace{1.5cm} % University name
\textsc{\Large MSc Project Report \\ 2017-2018}\\[0.5cm] % Thesis type

\HRule \\[0.4cm] % Horizontal line
{\Huge \bfseries \ttitle\par}\vspace{0.4cm} % Thesis title
\HRule \\[1.5cm] % Horizontal line

%\begin{minipage}[t]{0.4\textwidth}
%\begin{flushleft} \large
%\emph{Author:}\\
%\href{wangcc.me}{\authorname} % Author name - remove the \href bracket to remove the link
%\end{flushleft}
%\end{minipage}
%\begin{minipage}[t]{0.4\textwidth}
%\begin{flushright} \large
\emph{Supervisor:} \\
\href{https://www.lshtm.ac.uk/aboutus/people/palla.luigi}{\supname} % Supervisor name - remove the \href bracket to remove the link
%\end{flushright}
%\end{minipage}\\[3cm]
